### 2016-07-26 ms/ms.tex
added stuff

\section*{Introduction}
\label{sec:introduction}
\begin{itemize}
\item The structure of networks is related to ability of communities
  to maintain function in the face of species extinction.
\item A key restoration aim is to facilitate assembly of robust
  networks; thus it is critical to study how restoration
  influences the assembly of plant-pollinator interactions.
\item few theories about how networks assemble, preferential
  attachment 
\item To date, only two field studies have examined how networks
  assemble over time, often using space for time gradients.
\item \cite{Olesen2008} was investigated day-to-day, temporal assmebly
  of a plant-pollinator network within a season, taking advantage of
  the extreme seasonality of pollinator communities in Greenland.
  \cite{Olesen2008} found that within a season, the network assembly
  was similar to preferential attachment. New species tended to
  interact with already well-connected species, likely because these
  species are either more abundant or more temporally persistent.
\item Studying primary succession along a glacier foreland,
  \cite{albrecht2010plant} found a similar pattern where nestedness, a
  pattern of interactions where a generalist core interacts with both
  specialist and generalist species, increased as the community
  aged. % Studying ``managed succession'' of a clear-cut pine forest,
  % \cite{devoto2012understanding} found changes in network structure
  % were explained by a combination of age, tree density and variation
  % in tree diameter. 
\item Even non-succesional temporal dyanmics suggest a stable core of
  generalsits persiss despite high turnover of peripheral species
  \citep{fang2012relative, diaz2010changes, alarcon2008year}.
\item In contrast to the ordered netowrk build-up described by
  perferential attachment, assembly may be punctated by significant
  reorganizations of interactions. For example, as new species are
  added, resident species change their interaction parteners to
  minimize competition, or become extinct.
\end{itemize}

>>>>

\section*{Introduction}
\label{sec:introduction}
\begin{itemize}
\item The structure of networks is related to ability of communities
  to maintain function in the face of species extinction.
\item A key restoration aim is to facilitate assembly of robust
  networks; thus it is critical to study how restoration
  influences the assembly of plant-pollinator interactions.
\item few theories about how networks assemble, preferential
  attachmen. According to this model, a new species is more likely to
  interact with species that are already well-connected (''the
  rich-get-richer'' principle).
\item To date, only two field studies have examined how networks
  assemble over time, often using space for time gradients.
\item \cite{Olesen2008} was investigated day-to-day, temporal assmebly
  of a plant-pollinator network within a season, taking advantage of
  the extreme seasonality of pollinator communities in Greenland.
  \cite{Olesen2008} found that within a season, the network assembly
  was similar to preferential attachment. New species tended to
  interact with already well-connected species, likely because these
  species are either more abundant or more temporally persistent.
\item Studying primary succession along a glacier foreland,
  \cite{albrecht2010plant} found a similar pattern where nestedness, a
  pattern of interactions where a generalist core interacts with both
  specialist and generalist species, increased as the community
  aged. % Studying ``managed succession'' of a clear-cut pine forest,
  % \cite{devoto2012understanding} found changes in network structure
  % were explained by a combination of age, tree density and variation
  % in tree diameter. 
\item Even non-succesional temporal dyanmics suggest a stable core of
  generalsits persiss despite high turnover of peripheral species
  \citep{fang2012relative, diaz2010changes, alarcon2008year}.
\item In contrast to the ordered network build-up described by
  perferential attachment, assembly may be punctated by significant
  reorganizations of interactions. For example, as new species are
  added, resident species change their interaction parteners to
  minimize competition, or become extinct. Such significant
  reorganizations of interactions, or changing points, have been
  observed in networks \citep{peel2014detecting}.
